% Access Control in XML

\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{listings} % For XML code examples

\begin{document}
\title{XML Access Control: Models, Policies and Implementation}
\author{Biliuți Andrei \and Zara Mihnea-Tudor \and Roman Tudor}
\institute{"Alexandru Ioan Cuza" University of Iași, Iași IS 700132, Romania
\email{romantudor.contact@gmail.com}}
\maketitle

\begin{abstract}
This paper presents a comprehensive overview of XML access control mechanisms, including security models, policy frameworks, and implementation approaches. We examine various access control models specifically designed for XML documents, discuss policy specification languages and analyze practical implementation strategies for securing XML data.
\keywords{XML Security \and Access Control \and Role-Based Access Control \and XML Encryption.}
\end{abstract}

% 1. Introduction
\section{Introduction}
Here is the Introduction.

% 2. XML Access Control Models
\section{XML Access Control Models}

% 2.1. Basic Concepts
\subsection{Basic Concepts}
Write here about XML security fundamentals and access control basics.

% 2.2. Fine-Grained Access Control
\subsection{Fine-Grained Access Control}
Write here about XML element-level and attribute-level access control.

% 2.3. Role-Based Access Control for XML
\subsection{Role-Based Access Control for XML}
Write here about RBAC implementation in XML context.

% 3. Access Control Policy Languages
\section{Access Control Policy Languages}

% 3.1. XACML
\subsection{XACML}
Write here about XACML framework and implementation.

% 3.2. Custom Policy Specifications
\subsection{Custom Policy Specifications}
Write here about specialized XML security policy languages.

% 4. Implementation Approaches
\section{Implementation Approaches}

% 4.1. Enforcement Mechanisms
\subsection{Enforcement Mechanisms}
Write here about policy enforcement points and mechanisms.

% 4.2. Performance Considerations
\subsection{Performance Considerations}
Write here about optimization techniques and performance analysis.

% 5. Case Studies
\section{Case Studies}
Write here about practical implementations and real-world scenarios.

% 6. Conclusions
\section{Conclusions}
Write here about Conclusions.

% 7. Bibliography
\begin{thebibliography}{8}
\bibitem{damiani2002fine}
Damiani, E., et al.: A fine-grained access control system for XML documents. ACM Trans. Inf. Syst. Secur. 5(2), 169--202 (2002)

\bibitem{bertino2001authorization}
Bertino, E., Ferrari, E.: Secure and selective dissemination of XML documents. ACM Trans. Inf. Syst. Secur. 5(3), 290--331 (2002)

\bibitem{oasis2013extensible}
OASIS: eXtensible Access Control Markup Language (XACML) Version 3.0 (2013)

\bibitem{murata2006xml}
Murata, M., et al.: XML access control using static analysis. ACM Trans. Inf. Syst. Secur. 9(3), 292--324 (2006)

\end{thebibliography}
\end{document}